\plaintitle

### 2016-08-18 drafts/labor/cases.tex
cleaned up some comments
revs

\documentclass[trackingWork]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother
\begin{document}
\section{Major Research Questions}
% \al¬i{4 paragraphs on what happened in the above contexts; 2 paragraphs on best/worst outcomes \& why; ??? paragraphs on predictions for crowdsourcing}

%  _ _           _ _                __ 
% | (_)_ __ ___ (_) |_ ___    ___  / _|
% | | | '_ ` _ \| | __/ __|  / _ \| |_ 
% | | | | | | | | | |_\__ \ | (_) |  _|
% |_|_|_| |_| |_|_|\__|___/  \___/|_|

%                            _                          _             
%   ___ _ __ _____      ____| |___  ___  _   _ _ __ ___(_)_ __   __ _ 
%  / __| '__/ _ \ \ /\ / / _` / __|/ _ \| | | | '__/ __| | '_ \ / _` |
% | (__| | | (_) \ V  V / (_| \__ \ (_) | |_| | | | (__| | | | | (_| |
%  \___|_|  \___/ \_/\_/ \__,_|___/\___/ \__,_|_|  \___|_|_| |_|\__, |
%                                                               |___/

% let's do topic sentences!
\subsection{What are the limits of crowdsourcing?}
Research in crowdsourcing has spent the better part of a decade
exploring how to grow the limits of crowdsourcing and
find the boundaries of crowd work and microtasks;
this has largely involved
  identifying challenges to this form of labor,
  overcoming them through novel designs of work--flows and processes, and
  repeating the process
\cite{bernsteinSoylent}.
The question that has emerged
among these researchers and
through the work that they have produced then
has been driving at \textit{whether} there are limits to crowdsourcing
(and, if so, what factors determine those limits).
Through this lens, we can point to
a number of contributions to the field that have extended the boundaries of crowd work.

The exploration of crowdsourcing's potential and limits has principally looked at
manipulating and extending along three dimensions:
\begin{inlinelist}
  % \item \cref*{sec:Complexity},
  \item \nameref{sec:Complexity},
  \item \nameref{sec:Slicing}, and
  \item \nameref{sec:flexibility}
\end{inlinelist}.
We'll explore these aspects of crowdsourcing,
discussing the extents to which work can be
decomposed,
contextually abstracted, and
made more resilient to attrition of various forms.
We'll also point to corresponding piecework literature addressing these aspects.
Finally, we'll discuss how these elements will serve
to constrain the upper and lower bounds of crowdsourcing as it relates
to the question of the furthest limits of crowdsourcing.

%      _                                          _ _   _             
%   __| | ___  ___ ___  _ __ ___  _ __   ___  ___(_) |_(_) ___  _ __  
%  / _` |/ _ \/ __/ _ \| '_ ` _ \| '_ \ / _ \/ __| | __| |/ _ \| '_ \ 
% | (_| |  __/ (_| (_) | | | | | | |_) | (_) \__ \ | |_| | (_) | | | |
%  \__,_|\___|\___\___/|_| |_| |_| .__/ \___/|___/_|\__|_|\___/|_| |_|
%                                |_|                                  
%
% stronger topic sentences
% boosterist (???)

@@

% NEEDS TO GO ELSEWHERE
% \citeauthor{cheng2015break} found that microtasks
% --- though not necessarily \textit{faster} than ``macrotasks'' ---
% yield higher quality work,
% particularly when that work is susceptible to frequent interruptions
% \cite{cheng2015break}.

@@

\topic{A smaller but growing body of work has reflected on these bodies of work
and brought to our attention a number of ethical questions surrounding the
increasing complexity of crowdwork and the hazards that increasingly arise.}
\citeauthor{professionalCrowdworkEthics} bring some of these issues at stake
--- working for increasing amounts of time on tasks of growing complexity, only to discover that requesters are not willing to pay,
for instance ---
but these and other dangers range an enormous landscape % too informal?
\cite{crowdworkFuture,professionalCrowdworkEthics,nickerson2013crowd,dynamo}.

\topic{We summarize the work discussed so far in this way:
% crowdsourcing researchers have attempted to find the characteristics of crowdwork
researchers of crowdsourcing and on--demand labor in general
have attempted to find the characteristics which
enable and stymie successful applications of this form of work,
and how to get past or around these boundaries.}
Whether this work has focused on the self (as in the case of ``selfsourcing'')
or on others (as in \textit{CrowdForge} and \textit{Foundry}),
crowdsourcing literature has generally studied the constituent work
and attempted either to work around or indeed with the limitations of crowdwork to accomplish a difficult task
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016,crowdForgeKittur,foundry}.
% Following this thread of work, it may be said that
% much of the work in crowdsourcing has found ways of ``vertically slicing'' work
% such that each person is responsible for as small a task as can be made reasonable
% --- taking a minute of audio, for instance, and transcribing that.
% The findings we take away from the crowdsourcing literature might be summed up as
% a number of ways
% to break tasks down \cite[see][]{selfsourcingTeevan2014,foundry,crowdForgeKittur} and
% measuring the costs as they relate to work completion \&
% to a lesser extent to workers
% \cite[see][]{measuringCrowdsourcingCheng,cheng2015break,crowdworkFuture,professionalCrowdworkEthics}.

\topic{Research into piecework has explored similar limits,
with particularly striking parallels in
the language used to describe factors necessary for piecework to thrive.}
\citeauthor{10.2307/23702539} describe piecework in \citeyear{10.2307/23702539} as
``\dots~based on examination of various shop jobs,
which included calculation of the standard time and compensation for each task.
Most piecework plans required additional clerical and supervisory people
(such as piecework clerks, inspectors, and ``experts'')\dots'',
allowing for what the \textit{American Machinist} would later call ``paper efficiency'',
describing savings on paper that are in fact passed on to workers
\cite{10.2307/23702539}.
In this context,
the introspection of tasks by experts and the careful work assignment \& management of workers
we see in historical piecework seem to parallel crowdsourcing.

\citeauthor{Brown01041990} draws more decisive boundaries on piece rate approaches to remuneration,
identifying in analysis of data from
the U.S. Bureau of Labor and Statistics that
``larger establishment are less likely to use piece rates and predominantly female establishments more likely to do so; unionized establishments make significantly greater use of standard--rate pay than do nonunion establishments; \textit{incentive pay is less likely in jobs with a variety of duties than in jobs with a narrow set of routinized duties}; and the ease of monitoring work quality is correlated with the use of incentive pay''
\cite{Brown01041990}.

What's different today? We can turn to \citeauthor{10.2307/23702539}'s reflection on railroad piecework
for a hint of what might have enabled the future of crowdwork in which we now live:
``\dots~only the largest and most wealthy railroads stood to gain substantially from scientific management,
because only they had the resources to eliminate union resistance and
\textit{pay the overhead involved in installing work reorganization}''
(emphasis added)
\cite{10.2307/23702539}.

We argue that crowdsourcing is more widespread today,
and has the potential to become even larger in scale,
because the underlying architecture of crowdwork is digital;
reformulating workflows to decompose tasks and institute piecework compensation programs
is easier today than it was for railroad companies which had to move physical capital to do so.

\ali{\citeauthor{10.2307/23702539} later argues that a significant obstacle to the introduction of piecework in railroad shops was the resistance of workers
(the other being the resistance of management (for different and varying reasons)).
In the cases of online platforms like AMT and digitally mediated platforms like Uber,
where in both cases workers rarely if ever interact face--to--face and opportunities for coordination and collective action are severely limited,
we should expect to see the challenges stymieing collective action that we see in \citeauthor{dynamo} and elsewhere
\cite{10.2307/23702539,dynamo}.
}

%                     _            _         _                  _   _             
% __      _____  _ __| | __   __ _| |__  ___| |_ _ __ __ _  ___| |_(_) ___  _ __  
% \ \ /\ / / _ \| '__| |/ /  / _` | '_ \/ __| __| '__/ _` |/ __| __| |/ _ \| '_ \ 
%  \ V  V / (_) | |  |   <  | (_| | |_) \__ \ |_| | | (_| | (__| |_| | (_) | | | |
%   \_/\_/ \___/|_|  |_|\_\  \__,_|_.__/|___/\__|_|  \__,_|\___|\__|_|\___/|_| |_|
%

\subsubsection{Work Abstraction}\label{sec:Slicing}
Decomposition allows requesters to assign parallelized tasks
without undue concern for the broader context of the work.
The earlier example of transcribed audio is admittedly a carefully curated one
--- used to illustrate the ability
to parallelize work across as many workers as there are tasks ---
but even in this case problems arise;
breaking an hour--long interview into
3,600 1--second--long tasks would seem to make it impossible to do the tasks
for lack of \textit{context},
but the other extreme (one hour--long block)
offers no performance improvement over conventionally sourced work.

@@

\onlyinsubfile{
  \balance{}
  \printbibliography
  % \nobalance{}
  \clearpage
  \nobalance{}
  \begin{appendices}
  Points to make:
  \begin{itemize}
    \item Blossoming of piecework
    \begin{itemize}
      \item high point: consultants?
      \item most cases: auto workers/etc\dots
      \item worst case: sweatshops (especially in developing nations)
    \end{itemize}
    \item what led to these outcomes?
    \begin{itemize}
      \item ``consultant'' work came out well because the work was complex;
      this made it difficult to turn into a mass market commodity.
      We see consultants ranging skill levels like
      oDesk (implementing modules) to
      Accenture (on--demand teams of consultants).
      \item auto workers,
      working in settings where capital couldn't be moved as easily
      found themselves in the same workspace as a direct
      --- if multi--stepped ---
      result to the benefits of putting people in the same place to consolidate resources.
      Moreover,
      workers had leverage over factory owners as a result of that consolidated capital;
      operating equipment required training.
      \item sweatshop workers fared the worst,
      for reasons that may seem obvious with hindsight.
      Source materials for textiles are easier to ship than mechanical components such as engines,
      making it easier for factories to relocate to developing nations
      (where cost--of--living, and consequently wages, would be lower).
      As wages, CoLAs, and QoL rise, workers begin asking for
      (and later demanding)
      higher wages and better conditions.
      But where the auto workers have leverage,
      textile workers find only a precarious economic balance now tipped by their collective action,
      spurring manufacturers to move to a new locale
    \end{itemize}
  \end{itemize}

>>>>

\documentclass[trackingWork]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother
\begin{document}
\section{Major Research Questions}

\subsection{What are the limits of crowdsourcing?}
Research in crowdsourcing has spent the better part of a decade
exploring how to grow the limits of crowdsourcing and
find the boundaries of crowd work and microtasks;
this has largely involved
  identifying challenges to this form of labor,
  overcoming them through novel designs of work--flows and processes, and
  repeating the process
\cite{bernsteinSoylent}.
The question that has emerged
among these researchers and
through the work that they have produced then
has been driving at \textit{whether} there are limits to crowdsourcing
(and, if so, what factors determine those limits).
Through this lens, we can point to
a number of contributions to the field that have extended the boundaries of crowd work.

The exploration of crowdsourcing's potential and limits has principally looked at
manipulating and extending along three dimensions:
\begin{inlinelist}
  \item \nameref{sec:Complexity},
  \item \nameref{sec:Slicing}, and
  \item \nameref{sec:flexibility}
\end{inlinelist}.
We'll explore these aspects of crowdsourcing,
discussing the extents to which work can be
decomposed,
contextually abstracted, and
made more resilient to attrition of various forms.
We'll also point to corresponding piecework literature addressing these aspects.
Finally, we'll discuss how these elements will serve
to constrain the upper and lower bounds of crowdsourcing as it relates
to the question of the furthest limits of crowdsourcing.

@@

@@

\topic{A smaller but growing body of work has reflected on this
and brought to our attention a number of ethical questions surrounding the
increasing complexity of crowdwork and the hazards that increasingly arise.}
\citeauthor{professionalCrowdworkEthics} bring some of these issues at stake
--- working for increasing amounts of time on tasks of growing complexity, only to discover that requesters are not willing to pay,
for instance ---
but these and other dangers range an enormous landscape % too informal?
\cite{crowdworkFuture,professionalCrowdworkEthics,nickerson2013crowd,dynamo}.

\topic{We summarize the work discussed so far in this way:
researchers of crowdsourcing and on--demand labor in general
have attempted to find the characteristics which
enable and stymie successful applications of this form of work,
and how to get past or around these boundaries.}
Whether this work has focused on the self (as in the case of ``selfsourcing'')
or on others (as in \textit{CrowdForge} and \textit{Foundry}),
crowdsourcing literature has generally studied the constituent work
and attempted either to work around or indeed with the limitations of crowdwork to accomplish a difficult task
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016,crowdForgeKittur,foundry}.

% \topic{Research into piecework has also explored the limits of piecework,
% with some findings.}

\ali{

Talked to someone about this section and got some feedback\dots
\begin{enumerate}
  \item Explain what ``clever arrangement of work'' in the first paragraph means
        (should be simple; Find--Fix--Verify is the \textit{sort} of thing I mean);
  \item I should make the ``selfsourcing'' stuff clearer for people unfamiliar with it
        (maybe even to justify its placement here); and
  \item I should break up \citeauthor{10.2307/23702539} \& \citeauthor{Brown01041990}
        to make the historical stuff on piecework
        directly speak to the three previous paragraphs.
  \item (Maybe?) summarize the piecework stuff
        (the last paragraph approaches that, but more could be done).
\end{enumerate}
Thoughts on this?

}

% the language used to describe the factors considered for piecework to thrive.}
First, we look to
\citeauthor{10.2307/23702539},
who describes piecework as
    ``\dots~based on examination of various shop jobs,
    which included calculation of the standard time and compensation for each task''
\cite{10.2307/23702539}.
\citeauthor{10.2307/23702539} later enumerates some of the roles required
to facilitate piecework in the early \nth{20} century:
    ``\dots~piecework clerks, inspectors, and ``experts''\dots''
\cite{10.2307/23702539}.
\citeauthor{Brown01041990} makes a more assertive
claim about the factors necessary for piecework to thrive,
specifically arguing that
    ``\dots~incentive pay is less likely in jobs with
    a variety of duties than in jobs with a narrow set of routinized duties''
\cite{Brown01041990}.
\citeauthor{10.2307/23702539} makes another claim that
successful cases of piecework owed themselves in part to the fact that
    ``\dots~only [the largest and most wealthy railroads] had the resources to~\dots
    pay the overhead involved in installing work reorganization''
\cite{10.2307/23702539}.

\topic{Digital media have expanded the scope of viable piecework by pushing drastically on the limits
cited by piecework researchers.}
The research on piecework tells us that
we should expect piecework to thrive in industries where
the nature of the work is limited in complexity.
Given the flourishing of on--demand labor platforms such as
Uber, Amazon Mechanical Turk, and others, we ask ourselves
what --- if anything --- has changed.
We argue that the Internet has trivialized the costs and challenges of the earlier limiting factors for two reasons:
\begin{inlinelist}
  \item Technology make it much easier to do complex work aided by computers; and % is there a source for this? Is this necessary to cite?
  \item The Internet allows us to leverage the benefits of ``economies of scale'' at very little cost
        to the system--designer \cite{lessig2006code}
\end{inlinelist}.

\ali{\citeauthor{10.2307/23702539} also argues that
a significant obstacle to the introduction of piecework in railroad shops was
the resistance of workers
(the other being the resistance of management (for different and varying reasons)).
In the cases of online platforms like AMT and digitally mediated platforms like Uber,
where in both cases workers rarely
if ever
interact face--to--face and
opportunities for coordination and collective action are severely limited,
we should expect to see
the challenges stymieing collective action
that we see in \citeauthor{dynamo} and elsewhere
\cite{10.2307/23702539,dynamo}.}

\subsubsection{Slicing work smaller
\joke{ --- or ``putting the {\tiny `micro'} in microwork''}
}\label{sec:Slicing}

Decomposition allows requesters to assign parallelized tasks
without undue concern for the broader context of the work.
The earlier example of transcribed audio is admittedly a carefully curated one
--- used to illustrate the ability
to parallelize work across as many workers as there are tasks ---
but even in this case problems arise;
breaking an hour--long interview into
3,600 1--second--long tasks would seem to make it impossible to do the tasks
for lack of \textit{context},
but the other extreme (one hour--long block)
offers no performance improvement over conventionally sourced work.

@@

\onlyinsubfile{
  \balance{}
  \printbibliography
  % \nobalance{}
  \clearpage
  \nobalance{}
  \begin{appendices}
\section{Graveyard}

\citeauthor{cheng2015break} found that microtasks
--- though not necessarily \textit{faster} than ``macrotasks'' ---
yield higher quality work,
particularly when that work is susceptible to frequent interruptions
\cite{cheng2015break}.
